Batched Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-02-01 paper/experiments.tex
Paper update

% TODO: more details about the setup of experiments

The proposed MACE algorithm was compared with several state-of-the-art parallel
Bayesian optimization methods, including the BLCB algorithm, the local
penalization method with EI acquisition function (EI-LP), the qEI and the qKG
strategy. We implemented the BLCB algorithm while for other compared
algorithms, we used open source implementations\footnote{We implemented the
BLCB algorithm as the availble open source implementations only allow discrete
input; for the EI-LP method, the code is downloaded from
https://github.com/SheffieldML/GPyOpt is used; the code for qEI and qKG is
downloaded from https://github.com/wujian16/Cornell-MOE}.

@@

We tested the MACE algorithm and other parallel BO method using seven benchmark
functions, including the branin function, the alpine1 function, the 6D hartmann
function, the 2D and 10D ackley function and the 2D and 10D Rosenbrock
function. The dimensions and design space are summarized in
Table~ref{tab:summaryanalygical}.

\begin{table}[htbp]
    \centering
    \caption{Summary of the analytical benchmark functions}
    \label{tab:summaryanalygical}
    \begin{tabular}{llllllll}
        \toprule
        Function            & Dimension        & Search domain    \\ \midrule
         Branin             & 2                & $[-5,  10]\times[0, 15]$ \\
         Alpine1            & 5                & $[-10, 10]^5$           \\
         Hartmann6          & 6                & $[0,   1]^6$              \\
         Ackley2            & 2                & $[-32, 32]^2$           \\
         Ackley10           & 10               & $[-32, 32]^{10}$          \\
         Rosenbrock2        & 2                & $[-5,  10]^2$            \\
         Rosenbrock10       & 10               & $[-20, 20]^{10}$          \\
        \bottomrule
    \end{tabular}
\end{table}

For all functions except the two 10D functions, we set the number of initial
random sampling to $N_{init} = 20$ and the number of iterations to 45. Batch
size are set to $B = 1 $ and $B = 4$ respectively, the total number of function
evaluations is $N_{init} + B \times iter$. For the 10D ackley and 10D
rosenbrock functions, we set the number of initial sampling to $N_{init} = 100$
and the number of iterations is fixed to 175. The experiments were repeated for
ten times to average the random fluctuations.

@@

\begin{figure*}[htbp]
    \vskip 0.2in
    \begin{center}
        \centerline{\includegraphics[width=\linewidth]{./img/convplot.eps}}
        \caption{Optimization results of the benchmark functions\textcolor{red}{data still incomplete}}
        \label{fig:CovPlotBenchmark}
    \end{center}
    \vskip -0.2in
\end{figure*}

As can be seen in Figure~\ref{fig:CovPlotBenchmark}, the MACE strategy is
competitive in both sequential and batch setting. The qKG method performed not
good for these benchmark functions, in some functions, it was even outperformed
by the sequential EI and LCB.

Other algorithms gave acceptable solutions, while the MACE algorithm are
usually the best or second best algorithms for these benchmark functions.

@@

\FloatBarrier

>>>>

The proposed MACE algorithm was tested using eight benchmark functions and two
real-world circuits. Four state-of-the-art parallel Bayesian optimization
methods were compared, including the BLCB algorithm, the local penalization
method with EI acquisition function, the qEI and qKG methods\footnote{We
implemented the BLCB algorithm as the availble open source implementations only
allow discrete input; for the EI-LP method, the code is downloaded from
https://github.com/SheffieldML/GPyOpt is used; the code for qEI and qKG is
downloaded from https://github.com/wujian16/Cornell-MOE}.

@@

We tested the MACE algorithm and other parallel BO method using eight commonly used benchmark
functions, as summarized in Table~ref{tab:summaryanalygical}.

\begin{table}[htbp]
    \centering
    \caption{Summary of the analytical benchmark functions}
    \label{tab:summaryanalygical}
    \begin{tabular}{llllllll}
        \toprule
         Function           & Dimension        & Search domain             \\ \midrule
         Branin             & 2                & $[-5,  10]\times[0, 15]$  \\
         Alpine1            & 5                & $[-10, 10]^5$             \\
         Hartmann6          & 6                & $[0,   1]^6$              \\
         Eggholder          & 2                & $[-512, 512]^2$           \\
         Ackley2            & 2                & $[-32, 32]^2$             \\
         Ackley10           & 10               & $[-32, 32]^{10}$          \\
         Rosenbrock2        & 2                & $[-5,  10]^2$             \\
         Rosenbrock10       & 10               & $[-20, 20]^{10}$          \\
        \bottomrule
    \end{tabular}
\end{table}

For all functions except the two 10D functions, we set the number of initial
random sampling to $N_{init} = 20$ and the number of iterations to $N_{iter} =
45$. Batch size are set to $B = 4$, the total number of function evaluations is
$N_{init} + B \times N_{iter}$. For the 10D ackley and 10D rosenbrock functions, we
$N_{init} = 100$ and $N_{iter} = 175$. The experiments were repeated ten
times to average the random fluctuations.

We also compared MACE algorithm with the EI and LCB acquisition functions in
sequential mode, the sequential EI and LCB are implemented by setting the batch
size $B = 1$ for EI-LP and BLCB algorithms.

@@

\begin{figure*}[htbp]
    \vskip 0.2in
    \begin{center}
        \centerline{\includegraphics[width=1.0\linewidth]{./img/convplot.eps}}
        \caption{Optimization results of the benchmark functions}
        \label{fig:CovPlotBenchmark}
    \end{center}
    \vskip -0.2in
\end{figure*}

As can be seen in Figure~\ref{fig:CovPlotBenchmark}, when running with batch
size $B = 4$, the MACE algorithm gives the best performance for six out of the
eight benchmarks. For the 2D Ackley function, EI-LP is the best algorithm,
while for the Eggholder function, the MACE, BLCB and EI-LP have quite similar
performance. Compare the batched MACE and the sequential MACE, the speedup is
also dramatic.

@@
